Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-14 longoutput.tex
Change wording

Let $C$ undergo the above transformations so it has the following properties
\begin{itemize}
	\item All states are real (including initial, intermediate states, and output).
	\item Consists of only Hadamard and Toffoli gates
	\item The last $\gamma$ of the gates are all identity gates (can easily achieve by padding)
\end{itemize}

@@

According to \cite{2002quant.ph.10077A}, $H_{prop}\geq 0$ due to the above form being relevant to random walks. Furthermore, the second eigenvalue of $H_{prop}$ is at least $\frac{1}{2(T+1)^2}$.

>>>>

Let $C$ undergo the above transformations so it has the following properties
\begin{itemize}
	\item All states are real (including initial, intermediate states, and output).
	\item Consists of only Hadamard and Toffoli gates
	\item The last $\gamma$ of the gates are all identity gates (easily achievable by padding)
\end{itemize}

@@

According to \cite{2002quant.ph.10077A}, $H_{prop}\geq 0$ due to the above form being relevant to random walks. Furthermore, the last nonzero eigenvalue of $H_{prop}$ is at least $\frac{1}{2(T+1)^2}$.
